\documentclass[12pt, titlepage]{article}

\usepackage{float}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{hyperref}
\hypersetup{
    colorlinks,
    citecolor=black,
    filecolor=black,
    linkcolor=red,
    urlcolor=blue
}
\usepackage[round]{natbib}

\input{../Comments}
\input{../Common}

\begin{document}

\title{Verification and Validation Report: \progname} 
\author{\authname}
\date{\today}
	
\maketitle

\pagenumbering{roman}

\section{Revision History}

\begin{tabularx}{\textwidth}{p{3cm}p{2cm}X}
\toprule {\bf Date} & {\bf Version} & {\bf Notes}\\
\midrule
Date 1 & 1.0 & Notes\\
Date 2 & 1.1 & Notes\\
\bottomrule
\end{tabularx}

~\newpage

\section{Symbols, Abbreviations and Acronyms}

\renewcommand{\arraystretch}{1.2}
\begin{tabular}{l l} 
  \toprule		
  \textbf{symbol} & \textbf{description}\\
  \midrule 
  T & Test\\
  \bottomrule
\end{tabular}\\


\newpage

\tableofcontents

\listoftables %if appropriate

\listoffigures %if appropriate

\newpage

\pagenumbering{arabic}

This document presents the outcomes of the tests specified in the Verification and Validation (\href{https://github.com/rnorouziani/3D-H3C/blob/main/docs/VnVPlan/VnVPlan.pdf}{VnV}) Plan.

\section{Functional Requirements Evaluation}


This section evaluates the functionality of the 3D-H3C software, focusing on the verification of inputs and outputs against the specifications outlined in the System Requirements Specification (\href{https://github.com/rnorouziani/3D-H3C/blob/main/docs/SRS/SRS.pdf}{SRS}).

\subsection{T1: Test for Input Constraints}
\textbf{Description:} This test verifies that all input variables conform to the constraints specified in the \href{https://github.com/rnorouziani/3D-H3C/blob/main/docs/SRS/SRS.pdf}{SRS}. It ensures the software accepts only valid inputs which adhere to predefined criteria necessary for correct calculations within the 3D-H3C system.

\textbf{Responsible Unit Tests:} UT1 to UT16 cover a range of scenarios, from proper data loading and validation to ensuring correct initialization of different software modules. Detailed results of these unit tests are discussed in the \hyperref[sec:UT]{Unit Testing} section.

\subsection{T2: Test for Output Current Constraints}
\textbf{Description:} This test ensures that the output currents do not exceed the maximum acceptable values for each coil, as specified in the \href{https://github.com/rnorouziani/3D-H3C/blob/main/docs/SRS/SRS.pdf}{SRS}. This is crucial for preventing operational hazards and ensuring the system's safety and reliability.

\textbf{Responsible Unit Tests:} UT17 and UT18 focus on validating the outputs of the software. UT17 checks if currents within the specified range are valid, while UT18 tests responses when currents exceed permissible limits. Detailed results of these tests are provided in the \hyperref[sec:UT]{Unit Testing} section.

\subsection{T3: Test for Target Magnetic Force and Torque}
\textbf{Description:} This test validates that the calculated currents produce the target magnetic force and torque within the required accuracy, in accordance with the \href{https://github.com/rnorouziani/3D-H3C/blob/main/docs/SRS/SRS.pdf}{SRS}. This precision is essential for applications where exact magnetic outputs are critical.

\textbf{Responsible Unit Tests:} UT19 to UT21 assess various aspects of output accuracy. UT19 to UT21 verify that the outputs (force and torque) meet required accuracy levels. Details on the execution and outcomes of these tests are elaborated in the \hyperref[sec:UT]{Unit Testing} section.


\section{Nonfunctional Requirements Evaluation}

\subsection{Overview}
The evaluation of nonfunctional requirements is critical for ensuring that the system not only meets its functional specifications but also adheres to performance, usability, reliability, and other qualitative metrics that define a well-rounded and robust system. 

\subsection{Status of Evaluation}
As of the current development stage, the evaluation of nonfunctional requirements has not been conducted. The primary reason for this is the limited time available during the initial phases of the project. This section will be updated as evaluations are carried out and results become available.


\section{Unit Testing}

This section shows the results of running the unit tests as outlined in the Verification and Validation Plan (\href{https://github.com/rnorouziani/3D-H3C/blob/main/docs/VnVPlan/VnVPlan.pdf}{VnV plan}) documents.The results here confirm the successful execution of all outlined tests, demonstrating that each component of the software meets the functional specifications stated in the \href{https://github.com/rnorouziani/3D-H3C/blob/main/docs/VnVPlan/VnVPlan.pdf}{VnV plan}.


\subsection{CoilT Module Test}
\begin{small}
\begin{verbatim}

test_init_invalid_current (__main__.TestCoilT) ... ok
test_init_invalid_distance (__main__.TestCoilT) ... ok
test_init_invalid_radius (__main__.TestCoilT) ... ok
test_init_invalid_turns (__main__.TestCoilT) ... ok
test_init_valid (__main__.TestCoilT) ... ok

----------------------------------------------------------------------
Ran 5 tests in 0.000s
ok

\end{verbatim}
\end{small}


\subsection{InputFormat Module}
\begin{small}
\begin{verbatim}

test_create_coil_from_data_valid (__main__.TestInputFormat) ... ok
test_load_coils_file_not_found (__main__.TestInputFormat) ... ok
test_load_coils_invalid_json (__main__.TestInputFormat) ... ok
test_load_coils_valid (__main__.TestInputFormat) ... ok
test_load_params_invalid_combination (__main__.TestInputFormat) ... Error: Regarding the magnetic moment, the target magnetic torque or force is not achievable!
ok
test_load_params_invalid_magnetic_force (__main__.TestInputFormat) ... Error: Please enter exactly 3 values for the target magnetic force.
ok
test_load_params_invalid_magnetic_moment (__main__.TestInputFormat) ... Error: Exactly 3 values must enter for the magnetic moment vector.
ok
test_load_params_invalid_magnetic_torque (__main__.TestInputFormat) ... Error: Exactly 3 values must enter for the target magnetic torque.
ok
test_load_params_valid_input (__main__.TestInputFormat) ... ok

----------------------------------------------------------------------
Ran 9 tests in 0.011s
ok

\end{verbatim}
\end{small}

\subsection{MagneticCoreTest Module}
\begin{small}
\begin{verbatim}

test_calculate_current_of_target_force (__main__.TestMagneticCore) ... ok
test_calculate_current_of_target_torque (__main__.TestMagneticCore) ... ok
test_derivatives_of_magnetic_field_maxwell_at_center (__main__.TestMagneticCore) ... ok
test_initialization (__main__.TestMagneticCore) ... ok
test_magnetic_field_helmholtz (__main__.TestMagneticCore) ... ok
test_magnetic_force (__main__.TestMagneticCore) ... ok
test_magnetic_torque (__main__.TestMagneticCore) ... ok

----------------------------------------------------------------------
Ran 7 tests in 0.004s
OK


\end{verbatim}
\end{small}


\subsection{OutputVerification Module}
\begin{small}
\begin{verbatim}

test_calculate_similarity_opposite_direction (__main__.TestOutputVerification) ... ok
test_calculate_similarity_perfect_match (__main__.TestOutputVerification) ... ok
test_calculate_similarity_zero_vectors (__main__.TestOutputVerification) ... ok
test_is_accurate_enough_force_invalid (__main__.TestOutputVerification) ... ok
test_is_accurate_enough_torque_invalid (__main__.TestOutputVerification) ... ok
test_is_accurate_enough_valid (__main__.TestOutputVerification) ... ok
test_is_currents_within_range_invalid (__main__.TestOutputVerification) ... ok
test_is_currents_within_range_valid (__main__.TestOutputVerification) ... ok

----------------------------------------------------------------------
Ran 8 tests in 0.002s
OK


\end{verbatim}
\end{small}

\section{Trace to Requirements}
\begin{table}[H]
  \centering
  \caption{Relation of Test Cases to Requirements.}
  \vspace{2mm}
  \label{tab:req_trace}
  \begin{tabular}{|l|l|l|l|l|l|l|l|l|} % Corrected to include the correct number of columns
  \hline
     & R1 & R2 & R3 & R4 & NFR1 & NFR2 & NFR3 & NFR4 \\ \hline
  T1 & x  &    &    &    &      &      &      &      \\ \hline
  T2 &    &    &  x  &    &      &      &      &      \\ \hline
  T3 &    &  x  &    &    &      &      &      &      \\ \hline
  T4 &    &    &    &  x  &  x    &      &      &      \\ \hline
  T5 &    &    &    &    &      &   x   &      &      \\ \hline
  T6 &    &    &    &    &      &      &   x   &      \\ \hline
  T7 &    &    &    &    &      &      &      &   x   \\ \hline
  \end{tabular}
\end{table}
		
\section{Trace to Modules}		
\begin{table}[h]
  \centering
  \caption{Traceability Between Test Cases and Modules}
  \vspace{3mm}
  \label{tab:my-table}
  \begin{tabular}{l|c}
    Module         & Tests \\ \hline
    T1 & UT1 to UT21\\
    T2 & UT22, UT23\\
    T3 &  UT24 to UT29\\
  \end{tabular}
 \end{table}
\section{Code Coverage Metrics}
\begin{small}
\begin{verbatim}
Name                                              Stmts   Miss  Cover
---------------------------------------------------------------------
/home/reyhaneh/3D-H3C/src/CoilT.py                   15      0   100%
/home/reyhaneh/3D-H3C/src/InputFormat.py             50      2    96%
/home/reyhaneh/3D-H3C/src/MagneticCore.py            56      0   100%
/home/reyhaneh/3D-H3C/src/OutputVerification.py      40      2    95%
/home/reyhaneh/3D-H3C/src/__init__.py                 0      0   100%
TestCoilT.py                                         25      1    96%
TestInputFormat.py                                   61      1    98%
TestMagneticCore.py                                  48      1    98%
TestOutputVerification.py                            49      1    98%
---------------------------------------------------------------------
TOTAL                                               344      8    98%


\end{verbatim}
\end{small}
\bibliographystyle{plainnat}
\bibliography{../../refs/References}

\end{document}
